Template for GTEx example on cluster

### 2017-10-05 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

```{r}
sfares = readRDS("../data/GTExdata/SFAres/sfaGTExzscore.rds")
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:30){
  barplot(sfares$F[k,],main = paste("factor",k))
}

>>>>

```{r}
sfares = readRDS("../data/GTExdata/SFAres/sfaGTExzscore.rds")
# the F is K by N matrix! not N by K matrix
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:30){
  barplot(sfares$F[k,],main = paste("factor",k))
}
